An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
commit more concise algorithm

    \State $R = \{\}$ // rule set
    \State $\Pi$ // probabilities associated with rule set
    \For{each file $F$ in $C$}
      \State Initialize $opt$ flag.
      \For{each $z \in \theta \cup U$}
        \If{$z$ is a type} $opt = 1$
        \ElsIf{$z$ is an untyped spec} $opt = 0$
        \EndIf
        \State $Q$ contains candidate entries to pass on %
        \State $RM$ contains entries in remove set
        \If{opt}
          \State $Q = filter(F,\tau)$ 
          \State // Q contains $F$ entries with $\tau$ in type list
          \Else{$\enspace Q = F$}
        \EndIf
        \For{each entry $e$ in $Q$}
               \If{$g(e)$ is false}
                        \State continue to next entry
               \Else
                        \State $Y = \textrm{constructRules}(e, z, opt, Q \backslash RM)$
                        \State $R = R  \cup Y$
                        \State For each $r \in Y$, update $\Pi$ 
               \EndIf
               \State $RM = RM \cup e$
        \EndFor
     \EndFor
    \EndFor
%      \For{each $u \in U$}
%        \State $RM$ contains entries in remove set
%        \For{each entry $e$ in $F$}
%               \If{$g(e)$ is false}
%                        \State continue to next entry
%                        \Else 
%                        \State $CR = \textrm{constructURules}(e, u, F \backslash RM)$
%                        \State $R = R  \cup CR$
%                        \State For each $r \in CR$, update $\Pi$ 
%               \EndIf
%               \State $RM = RM \cup e$
%        \EndFor
%     \EndFor
%    \EndFor
    \State return $(\Pi,R)$
  \end{algorithmic}
\end{footnotesize}
\end{algorithm}

\begin{algorithm}[t]
\caption{Construct Template Rules}
\label{alg:crules}
\begin{footnotesize}
  \begin{algorithmic}[1]
  \State \textbf{constructTRules}($e, \tau, S$):\\
    Input: entry $e$ from intermediate representation\\ 
     \qquad \enspace \enspace type $\tau$\\
     \qquad \enspace \enspace set of entries $S$\\
     $R = \{\}$
     \For{each $t \in templates(\tau)$}
        \State Let $n$ be the arity of $t$.
        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
        \For{each $p \in P$}
         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
           \For{$i = 1:n$}
           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
           \State $r = \textrm{constructTRule}(v)$ 
            \If{$r$ is satisfied}
              $R = R \cup r$
            \EndIf
          \EndFor
        \EndFor
     \EndFor
     \State return $R$
  \end{algorithmic}
\end{footnotesize}
\end{algorithm}

@@

\begin{algorithm}[t]
\caption{Construct Untyped Specification Rules}
\label{alg:curules}
\begin{footnotesize}
  \begin{algorithmic}[1]
  \State \textbf{constructURules}($e, u, S$):\\
    Input: entry $e$ from intermediate representation\\ 
     \qquad \enspace \enspace untyped specification $u$\\
     \qquad \enspace \enspace set of entries $S$\\
     $R = \{\}$
        \State Let $n$ be the arity of $t$.
        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
        \For{each $p \in P$}
         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
           \For{$i = 1:n$}
           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
           \State $r = \textrm{constructURule}(v)$ 
            \If{$r$ is satisfied}
              $R = R \cup r$
            \EndIf
          \EndFor
        \EndFor
     \State return $R$
  \end{algorithmic}
\end{footnotesize}
\end{algorithm}

>>>>

    \State $R = \{\}$ // rule set
    \State $\Pi$ // probabilities associated with rule set
    \For{each file $F$ in $C$}
      \State Initialize $opt$ flag.
      \For{each $z \in \theta \cup U$}
        \State $Q$ contains candidate entries to consider
        \State $RM$ contains entries in remove set
        \If{$z$ is a type} \State $opt = 1$ \State $Q = filter(F,\tau)$
          \State // Q contains $F$ entries with $\tau$ in type list
        \ElsIf{$z$ is an untyped spec} \State $opt = 0$ \State $Q = F$
        \EndIf
        \For{each entry $e$ in $Q$}
               \If{$g(e)$ is false}
                        \State continue to next entry
               \Else
                        \State $CR = \textrm{constructRules}(e, z, opt, Q \backslash RM)$
                        \State $R = R  \cup CR$
                        \State For each $r \in CR$, update $\Pi$
               \EndIf
               \State $RM = RM \cup e$
        \EndFor
     \EndFor
    \EndFor
    \State return $(\Pi,R)$
  \end{algorithmic}
\end{footnotesize}
\end{algorithm}

\begin{algorithm}[t]
\caption{Construct Rules}
\label{alg:crules}
\begin{footnotesize}
  \begin{algorithmic}[1]
 \State \textbf{constructRules}($e, z, opt, S$):\\
    Input: entry $e$ from intermediate representation\\
     \qquad \enspace \enspace type or untyped specification $z$\\
     \qquad \enspace \enspace option $opt$, set to 1 if template\\
     \qquad \qquad \enspace \enspace \enspace \enspace \qquad or 0 if untyped spec\\
     \qquad \enspace \enspace set of entries $S$\\
     \State $R = \{\}$
     \State Set $j$ as an iteration variable.
     \If{opt == 1}
        \State iterate the following sequence \textbf{L} over all elements of $templates(z)$ 
        \State \ie, $j \in templates(z)$
     \ElsIf{opt == 0}
        \State $j = z$
     \EndIf
     \State Beginning of \textbf{L}: 
     \State Let $n$ be the arity of $j$.
      \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$.
      \For{each $p \in P$}
        \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
         \For{$i = 1:n$}
         \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
         \State $r = \textrm{constructRule}(v)$
         \If{$r$ is satisfied}
                $R = R \cup r$
         \EndIf
        \EndFor
     \EndFor
     \State End of \textbf{L}. 
     \State return $R$
  \end{algorithmic}
\end{footnotesize}
\end{algorithm}

@@
